\documentclass[review]{elsarticle}
%\documentclass[final,5p,times]{elsarticle}

\usepackage{lineno,hyperref}
\modulolinenumbers[1]

\usepackage{amsmath}
%%\usepackage[utf8]{inputenc}

\usepackage{graphicx}
\usepackage{multicol}
\usepackage{amsmath}
\usepackage{float} % Required for tables and figures in the multi-column environment - they need to be placed in specific locations with the [H] (e.g. \begin{table}[H])
\usepackage{multirow}
\usepackage{subcaption}% To use subfigures

%%To add notes un red to my text
\usepackage{xcolor}
\newcommand\mynote[1]{\textcolor{red}{#1}}
%\newcommand\myworries[1]{\textcolor{red}{#1}}
%%Example: \myworries{But I'm worried about the text}
%And then if you want to hide the comments, just add the
%line \renewcommand\myworries[1]{} below the \newcommand.
%This will hide all your notes
\renewcommand\mynote[1]{}

%Notes on margin page
\usepackage{geometry}
\usepackage{marginnote}
% \marginnote{This is a margin note using the geometry package, set at 3cm vertical offset to the line it is typeseted.}[3cm]
%\reversemarginpar
%\marginnote{This is a margin note using the geometry package, set at 5cm
%	vertical offset to the first line it is typeset.}[3cm]

%to do notes in the text
%%  \usepackage[colorinlistoftodos]{todonotes}
%%To hidde comment the last comand and uncomment the command bellow
\usepackage[disable]{todonotes}
 %%\todo{Here's a comment in the margin!}
 %%\todo[inline, color=green!40]{This is an inline comment.}
 
 %%place figures inside section
\usepackage{placeins}

\journal{Journal}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{lineno}
\usepackage{graphicx}

%\usepackage{vervatim}
%\hyperlinking
\begin{document}

%\tableofcontents
\linenumbers

\begin{frontmatter}

\title{Performance of the ALICE Diffractive detector in a beam-test.}
%%\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}

%% Group authors per affiliation:
%\author{AD collaboration}
%\author{Solangel Rojas Torres}
%\address{Radarweg 29, Amsterdam}
%\fntext[myfootnote]{Since 1880.}

%% or include affiliations in footnotes:
%\author[rt.solangel@gmail.com,solangel.rojas.torres@cern.ch]{Universidad Aut\'onoma de Sinaloa}
%\ead[url]{www.elsevier.com}

\author[uas]{Solangel Rojas Torres}
\ead{rt.solangel@gmail.com,solangel.rojas.torres@cern.ch}
\author[uas]{Ildefonso Le\'on Monz\'on}
\author[uas]{Carlos Duarte Galvan}
\author[uas]{Lucina Gabriela Espinoza Beltr\'an}
\author[uas]{Juan Carlos Cabanillas Noris}
\author[civestav]{Gerardo Herrera Corral}
\author[csr]{Jean-Pierre Revol}
\author[thn]{Christoph Mayer}
\author[ctu]{Michal Broz}
\author[buap]{Mario Iv\'an Mart\'inez Hernandez}
\author[buap]{Lu\'is Alberto Perez Moreno}
\author[buap]{Abraham Villatoro Tello}
\author[buap]{Arturo Fern\'andez T\'ellez}
\author[buap]{Mario Rodr\'iguez Cahuantzi}
\author[Helsinki0,Helsinki1]{Risto Orava}
\author[Helsinki0]{Mikael Mieskolainen}
\author[pucp]{Alberto Mart\'in Gago Medina}
\author[pucp]{Ernesto Calvo Villar}
\author[pucp]{Eric Endress}
\author[Helsinki0]{Dmitry Finogeev}
\author[inr]{Alexander Kurepin}
\author[inr]{Alexey Kurepin}
\author[inr]{Nikolay Kurepin}
\author[inr]{Andrey Reshetin}
\author[inr]{Arseniy Shabanov}
\author[inr]{Evgueni Usenko}
\author[seul]{Taesoo Kim}
%\author[]{}
%\ead{email2@domain.ca}
%\ead{email3@domain.ca}

\address[uas]{\textit{Universidad Aut\'onoma de Sinaloa},CULIACAN, M\'exico}
\address[buap]{\textit{Benem\'erita Univ. Aut\'onoma de Puebla},PUEBLA, M\'exico}
\address[civestav]{\textit{Centro de Investigación y de Estudios Avanzados del IPN}, C.D. M\'EXICO, M\'exico}
\address[csr]{Centro Studi e Ricerche ``Enrico Fermi'', ROMA, Italy}
\address[thn]{\textit{The Henryk Niewodniczanski Inst. of Nucl. Physics Polish Academy of Sciences}, CRACOW, Poland}
\address[seul]{\textit{Yonsei University}, SEOUL, South Korea}
\address[ctu]{\textit{Czech Technical University of Prague}, PRAHA, Czech Republic}
\address[Helsinki0]{\textit{Helsinki Inst. of Physics}, HELSINKI, Finland} 
\address[Helsinki1]{\textit{The University of Helsinki}, HELSINKI, Finland} 
\address[pucp]{\textit{Pontificia Universidad Cat\'olica del Per\'u}, LIMA, Per\'u}
\address[inr]{\textit{Russian Academy of Sciences, Inst. for Nuclear Research}, MOSCOW, Russia}

\begin{abstract}
	The ALICE Diffractive detector (AD) is a forward detector that was added to ALICE to extend the acceptance of
	the experiment in the forward rapidity region in order to improve the sensitivity for diffraction physics, for
	the measurement of the inelastic proton-proton cross-section, and to provide additional measurements of
	centrality in Pb-Pb, proton-Pb and Xe-Xe collisions. The AD is used as a trigger as well as a beam quality
	monitor at Point 2 of the LHC. AD consists of two assemblies, ADA and ADC, each station consist of two layers
	of scintillators. 
	Two detector modules identical to those installed in the experiment were tested in the PS T10 secondary beam at CERN, at beam momenta 1, 1.5, 2 and 6 GeV/c. The purpose was to check the uniformity of the efficiency
	across the detector modules, and measure the relative response to protons, pions and muons, therefore study
	the time and charge response. In addition, an attempt was made to obtain an absolute charge calibration of the
	detector.
\begin{comment}
Diffractive physics is a field of high energy physics whose have a great chances for new discoveries. The use
of an instrument designed specifically for such propose can extend the capabilities of ALICE experiment at CERN
to do research on the field. ALICE Diffractive detector was designed for such propose increasing the pseudorapidity 
coverage of ALICE therefore the probability to detect a phenomena not seen before. It was tested in T10 beam-line 
facilities  placed at CERN
and provide a source of particles. Were performed a set of measurement at 1, 1.5, 2 and 6 GeV/c beam momentum to measure
the time properties and light yielding of the different elements of the detector assemble. Some corrections techniques
were applied and the results were compared with the performance of the detector already installed in ALICE experiment. 
We show that the detector have the capability to detect minimum ionization particles with a good separation of the
noise level (pedestal) and the time resolution achieved fulfill the requirements for the research.
content...
\end{comment}
\end{abstract}

\begin{keyword}
ALICE\sep Diffractive physics  %\sep Particle detector \sep Beam test 
\sep Performance of High Energy Physics Detectors
%\sep Scintillators
%\sep Time resolution
%\MSC[2016] 00-01\sep  99-00
\end{keyword}

\end{frontmatter}


\input{NIM-tex/introduction_v0.tex}
%\input{NIM-tex/ADdetector_v0.tex}
\input{NIM-tex/expSetup_v3.tex}
\input{NIM-tex/DataSamples_v3.tex}
\input{NIM-tex/results_v3.tex}
\input{NIM-tex/conclusion_v0.tex}
%\newpage \clearpage
%\input{NIM-tex/appendix_v0.tex}

%\newpage 
%\clearpage
\pagebreak
\bibliography{ref}


\end{document}
